The Application of Magnetic Susceptibility Separation for Measuring Cerebral Oxygenation in Preterm Neonates

### 2025-03-31 _tex/index.tex
Built site for gh-pages

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\newsavebox\pandoc@box
\newcommand*\pandocbounded[1]{% scales image to fit in text height/width
  \sbox\pandoc@box{#1}%
  \Gscale@div\@tempa{\textheight}{\dimexpr\ht\pandoc@box+\dp\pandoc@box\relax}%
  \Gscale@div\@tempb{\linewidth}{\wd\pandoc@box}%
  \ifdim\@tempb\p@<\@tempa\p@\let\@tempa\@tempb\fi% select the smaller of both
  \ifdim\@tempa\p@<\p@\scalebox{\@tempa}{\usebox\pandoc@box}%
  \else\usebox{\pandoc@box}%
  \fi%
}
% Set default figure placement to htbp
\def\fps@figure{htbp}
\makeatother

@@

\raggedbottom
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{\textbf{Figure}}
\else
  \newcommand\figurename{\textbf{Figure}}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{\textbf{Table}}
\else
  \newcommand\tablename{\textbf{Table}}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\captionsetup{labelsep=period}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother

\usepackage[]{natbib}
\bibliographystyle{plainnat}
\usepackage{bookmark}

@@

\textsubscript{Source:
\href{https://WeberLab.github.io/Chisep_CSVO2_Manuscript/index.qmd.html}{Article
Notebook}}

\textsubscript{Source:
\href{https://WeberLab.github.io/Chisep_CSVO2_Manuscript/index.qmd.html}{Article
Notebook}}

\textsubscript{Source:
\href{https://WeberLab.github.io/Chisep_CSVO2_Manuscript/index.qmd.html}{Article
Notebook}}

@@

\textsubscript{Source:
\href{https://WeberLab.github.io/Chisep_CSVO2_Manuscript/index.qmd.html}{Article
Notebook}}

@@

\pandocbounded{\includegraphics[keepaspectratio]{index_files/figure-latex/notebooks-Figures-fig-graph-output-1.png}}

@@

\textsubscript{Source:
\href{https://WeberLab.github.io/Chisep_CSVO2_Manuscript/notebooks/Figures-preview.html\#cell-fig-graph}{Python
Figures}}

@@

\pandocbounded{\includegraphics[keepaspectratio]{index_files/figure-latex/notebooks-Figures-fig-masks-output-1.png}}

@@

\textsubscript{Source:
\href{https://WeberLab.github.io/Chisep_CSVO2_Manuscript/notebooks/Figures-preview.html\#cell-fig-masks}{Python
Figures}}

@@

\pandocbounded{\includegraphics[keepaspectratio]{index_files/figure-latex/notebooks-Figures-fig-sample-output-1.png}}

@@

\textsubscript{Source:
\href{https://WeberLab.github.io/Chisep_CSVO2_Manuscript/notebooks/Figures-preview.html\#cell-fig-sample}{Python
Figures}}

@@

\pandocbounded{\includegraphics[keepaspectratio]{index_files/figure-latex/notebooks-gavin_thesis_markdown-fig-methodplot-output-1.png}}

@@

\textsubscript{Source:
\href{https://WeberLab.github.io/Chisep_CSVO2_Manuscript/notebooks/gavin_thesis_markdown-preview.html\#cell-fig-methodplot}{gavin\_thesis\_R}}

@@

\pandocbounded{\includegraphics[keepaspectratio]{index_files/figure-latex/notebooks-gavin_thesis_markdown-fig-regionplot-output-1.png}}

@@

\textsubscript{Source:
\href{https://WeberLab.github.io/Chisep_CSVO2_Manuscript/notebooks/gavin_thesis_markdown-preview.html\#cell-fig-regionplot}{gavin\_thesis\_R}}

>>>>

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother

@@

\raggedbottom
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{\textbf{Figure}}
\else
  \newcommand\figurename{\textbf{Figure}}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{\textbf{Table}}
\else
  \newcommand\tablename{\textbf{Table}}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\captionsetup{labelsep=period}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[]{natbib}
\bibliographystyle{plainnat}
\usepackage{bookmark}

@@

\textsubscript{Source:
\href{https://WeberLab.github.io/Chisep_CSVO2_Manuscript/index-preview.html}{Article
Notebook}}

\textsubscript{Source:
\href{https://WeberLab.github.io/Chisep_CSVO2_Manuscript/index-preview.html}{Article
Notebook}}

\textsubscript{Source:
\href{https://WeberLab.github.io/Chisep_CSVO2_Manuscript/index-preview.html}{Article
Notebook}}

@@

\textsubscript{Source:
\href{https://WeberLab.github.io/Chisep_CSVO2_Manuscript/index-preview.html}{Article
Notebook}}

@@

\includegraphics{index_files/figure-latex/notebooks-Figures-fig-graph-output-1.png}

@@

\textsubscript{Source:
\href{https://WeberLab.github.io/Chisep_CSVO2_Manuscript/notebooks/Figures.ipynb.html\#cell-fig-graph}{Python
Figures}}

@@

\includegraphics{index_files/figure-latex/notebooks-Figures-fig-masks-output-1.png}

@@

\textsubscript{Source:
\href{https://WeberLab.github.io/Chisep_CSVO2_Manuscript/notebooks/Figures.ipynb.html\#cell-fig-masks}{Python
Figures}}

@@

\includegraphics{index_files/figure-latex/notebooks-Figures-fig-sample-output-1.png}

@@

\textsubscript{Source:
\href{https://WeberLab.github.io/Chisep_CSVO2_Manuscript/notebooks/Figures.ipynb.html\#cell-fig-sample}{Python
Figures}}

@@

\includegraphics{index_files/figure-latex/notebooks-gavin_thesis_markdown-fig-methodplot-output-1.png}

@@

\textsubscript{Source:
\href{https://WeberLab.github.io/Chisep_CSVO2_Manuscript/notebooks/gavin_thesis_markdown.qmd.html\#cell-fig-methodplot}{gavin\_thesis\_R}}

@@

\includegraphics{index_files/figure-latex/notebooks-gavin_thesis_markdown-fig-regionplot-output-1.png}

@@

\textsubscript{Source:
\href{https://WeberLab.github.io/Chisep_CSVO2_Manuscript/notebooks/gavin_thesis_markdown.qmd.html\#cell-fig-regionplot}{gavin\_thesis\_R}}
